### 2022-11-21 chapters/optimization/python-dir/python.tex
add : citing the interns work

\subsection{Python for Machine Learning}\label{sec:ml}
Machine learning is becoming an integral part of our daily lives, growing more potent and energy-hungry each year.
As machine learning can significantly impact climate change, it is vital to investigate mitigation techniques.

@@

\begin{figure}
    \centering
    \includegraphics[width=1.1\textwidth]{imgs/accuracy_basedonepoch}
    \caption{Accuracy along epochs.}
    \label{fig:eopochvsaccuracy}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1.1\textwidth]{imgs/cumulative_energy_vs_accuracy}
    \caption{Cumulative energy consumption vs. accuracy.}
    \label{fig:cum_energy_vs_accuracy}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1.1\textwidth]{imgs/cumulative_energy_fast10.pdf}
    \caption{Average energy for training the model based on the strategy.}
    \label{fig:av_energy_setup}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1.1\textwidth]{imgs/power_gpu_baedonepoche.pdf}
    \caption{Evolution of average GPU power along epochs.}
    \label{fig:ephoch_power}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1.1\textwidth]{imgs/epoch_duration.pdf}
    \caption{Distribution of the durations of each epoch.}
    \label{fig:epoch_duration}
\end{figure}

@@

%% REMARQUE the experiment with joulehunter isn't conducted within the same machine that is used for generating the boxplot graphs 
% We have chosen Django as our web framework.
Therefore, we chose to study if the choice of the database and the ORM impact energy consumption and web application performance.
% \subsection{Experiment \& Results}
To accomplish so, we examined the cost of a single request of the prior website using various ways to extract data from the database.
We considered using two different databases, \textsc{PostgreSQL} and \textsc{SQlite3}, that store the same records and three different ways to fetch the records:
\begin{enumerate}
    \item \textsf{Vanilla} relies only on the ORM to retrieve the data,
    \item \textsf{Prefetch} queries the data before being requested,
    \item \textsf{Optimized} leverages SQL without passing by the ORM.
\end{enumerate}

@@

\subsection{Python for Data Processing}
Another field of investigation is the type of data and control structures that might impact energy consumption.
In this study, we will run some common algorithms with different data structures and control structures to study if there is any difference in energy consumption.
\subsubsection{Experimental Protocol}
All of the tests in this study are done on the Grid5000 cluster using the same machine, Python interpreter, and library version.
Due to PowerAPI's frequency constraint, we measure the energy of $1,000$ algorithm iterations for each test.
Furthermore, we perform each test 20 times for completeness, deleting the cache between each run.
The data is then averaged and presented in graphs.

@@

\begin{figure}[!htb]
    \centering
    \includegraphics[width=\linewidth]{imgs/python_iterations}
    \caption{Comparison of the energy consumption of different Python loops.}
    \label{fig:pythonloops}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=.9\linewidth]{imgs/python_treatemens}
    \caption{Comparison of the energy consumption of different methods to convert a list.}
    \label{fig:pythontreatement}
\end{figure}

>>>>

\subsection{Python for Machine Learning}\label{sec:ml}
Machine learning is becoming an integral part of our daily lives, growing more potent and energy-hungry each year.
As machine learning can significantly impact climate change, it is vital to investigate mitigation techniques.
This part highlights the work of \citeauthor{kaminetzky_energy_2021}~\cite{kaminetzky_energy_2021} during his internship at inria

@@

\begin{figure}
    \centering
    \includegraphics[width=1.1\textwidth]{imgs/accuracy_basedonepoch}
    \caption{Accuracy along epochs~\cite{kaminetzky_energy_2021}.}
    \label{fig:eopochvsaccuracy}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1.1\textwidth]{imgs/cumulative_energy_vs_accuracy}
    \caption{Cumulative energy consumption vs. accuracy~\cite{kaminetzky_energy_2021}.}
    \label{fig:cum_energy_vs_accuracy}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1.1\textwidth]{imgs/cumulative_energy_fast10.pdf}
    \caption{Average energy for training the model based on the strategy~\cite{kaminetzky_energy_2021}.}
    \label{fig:av_energy_setup}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1.1\textwidth]{imgs/power_gpu_baedonepoche.pdf}
    \caption{Evolution of average GPU power along epochs~\cite{kaminetzky_energy_2021}.}
    \label{fig:ephoch_power}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1.1\textwidth]{imgs/epoch_duration.pdf}
    \caption{Distribution of the durations of each epoch~\cite{kaminetzky_energy_2021}.}
    \label{fig:epoch_duration}
\end{figure}

@@

%% REMARQUE the experiment with joulehunter isn't conducted within the same machine that is used for generating the boxplot graphs 
% We have chosen Django as our web framework.
Therefore, we chose to study if the choice of the database and the ORM impact energy consumption and web application performance.
% \subsection{Experiment \& Results}
To accomplish so, we examined the cost of a single request from the prior website using various ways to extract data from the database.
We considered using two different databases, \textsc{PostgreSQL} and \textsc{SQlite3}, that store the same records and three different ways to fetch the records:
\begin{enumerate}
    \item \textsf{Vanilla} relies only on the ORM to retrieve the data,
    \item \textsf{Prefetch} queries the data before being requested,
    \item \textsf{Optimized} leverages SQL without passing by the ORM.
\end{enumerate}

@@

\subsection{Python for Data Processing}
Another field of investigation is the type of data and control structures that might impact energy consumption.
In this study, we will run some common algorithms with different data structures and control structures to study if there is any difference in energy consumption.
This part displays the work of \citeauthor{randrianaina_optimisation_2019}\cite{randrianaina_optimisation_2019} during his internship at Inria.

\subsubsection{Experimental Protocol}
All of the tests in this study are done on the Grid5000 cluster using the same machine, Python interpreter, and library version.
Due to PowerAPI's frequency constraint, we measure the energy of $1,000$ algorithm iterations for each test.
Furthermore, we perform each test 20 times for completeness, deleting the cache between each run.
The data is then averaged and presented in graphs.

@@

\begin{figure}[!htb]
    \centering
    \includegraphics[width=\linewidth]{imgs/python_iterations}
    \caption{Comparison of the energy consumption of different Python loops~\cite{randrianaina_optimisation_2019}.}
    \label{fig:pythonloops}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=.9\linewidth]{imgs/python_treatemens}
    \caption{Comparison of the energy consumption of different methods to convert a list~\cite{randrianaina_optimisation_2019}.}
    \label{fig:pythontreatement}
\end{figure}
